---
params:
  title: 'A Title'
  subtitle: "A Subtitle"
  author: "Mickaël Canouil, *Ph.D.*"
  institute: "Inserm U1283 / CNRS UMR8199 / Institut Pasteur de Lille"
  date: !r format(Sys.time(), "%B %d, %Y")
  theme: "rlille"
output:
  xaringan::moon_reader:
    includes:
      after_body: 
    self_contained: true
    seal: false
    css: [default, css/rlille.css, css/mc-fonts.css]
    nature:
      highlightStyle: github
      highlightLines: true
      ratio: "16:9"
      countIncrementalSlides: false
title: '`r params[["title"]]`'
subtitle: '`r params[["subtitle"]]`'
author: '`r params[["author"]]`'
institute: '`r params[["institute"]]`'
date: '`r params[["date"]]`'
---

class: title-slide center middle

<style type="text/css">
:root {
  --main-logo: url(https://raw.githubusercontent.com/mcanouil/hex-stickers/master/SVG/rlille.svg);
}
</style>

<div class="main-logo"></div>
<div>
  <script>
    (function () {
      let tries = 0
      function addLogo () {
        if (typeof slideshow === 'undefined') {
          tries += 1
          if (tries < 10) {
            setTimeout(addLogo, 100)
          }
        } else {
          document.querySelectorAll('.remark-slide-content:not(.title-slide):not(.inverse):not(.hide_logo)')
            .forEach(function (slide) {
              const logo = document.createElement('a')
              logo.classList = 'logo'
              slide.appendChild(logo)
            })
        }
      }
      document.addEventListener('DOMContentLoaded', addLogo)
    })()
  </script>
</div>

# `r params[["title"]]`

## `r params[["subtitle"]]`

### `r params[["author"]]`

### `r params[["institute"]]`

### `r params[["date"]]`

---

```{r setup, include = FALSE}
options("width" = 110)
options(htmltools.dir.version = FALSE)


### Load Packages ==================================================================================
suppressPackageStartupMessages({
  library(here)
  library(knitr)
  library(ragg)
  library(svglite)
  library(ggplot2)
  library(ggtext)
  library(patchwork)
  library(data.table)
  library(showtext)
  library(xaringanExtra)
})


### knitr settings =================================================================================
opts_chunk$set(
  eval = TRUE,
  include = TRUE,
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  tidy = FALSE,
  crop = TRUE,
  autodep = TRUE,
  # results = "asis",
  width = getOption("width"),
  comment = "#>", 
  cache = FALSE, 
  fig.align = "center",
  fig.width = 11.5,
  fig.height = 5.75, 
  dpi = 150,
  dev = "svglite", 
  dev.args = list(
    web_fonts = list("https://fonts.googleapis.com/css?family=Alegreya+Sans")
  )
)
font_add_google("Alegreya Sans", "Alegreya Sans", regular.wt = 300)
showtext_auto()


### Tables and Figures Theme =======================================================================
theme_black <- function(
  base_size = 11,
  base_family = "",
  base_line_size = base_size / 22,
  base_rect_size = base_size / 22,
  theme = "mc"
) {
  bc <- switch(EXPR = theme,
    "mc" = c("#333333", "#7F7F7F", "#FFFFFF"),
    "rlille" = c("#F2F2F2", "#CCCCCC", "#D40000")
  )
  half_line <- base_size / 2
  ggplot2::theme(
    line = ggplot2::element_line(
      colour = bc[3],
      size = base_line_size,
      linetype = 1,
      lineend = "butt"
    ),
    rect = ggplot2::element_rect(
      fill = bc[1],
      colour = bc[3],
      size = base_rect_size,
      linetype = 1
    ),
    text = ggplot2::element_text(
      family = base_family,
      face = "plain",
      colour = bc[3],
      size = base_size,
      lineheight = 0.9,
      hjust = 0.5,
      vjust = 0.5,
      angle = 0,
      margin = ggplot2::margin(),
      debug = FALSE
    ),
    title = NULL,
    aspect.ratio = NULL,

    axis.title = NULL,
    axis.title.x = ggplot2::element_text(margin = ggplot2::margin(t = half_line), vjust = 1),
    axis.title.x.top = ggplot2::element_text(margin = ggplot2::margin(b = half_line), vjust = 0),
    axis.title.x.bottom = NULL,
    axis.title.y = ggplot2::element_text(angle = 90, margin = ggplot2::margin(r = half_line), vjust = 1),
    axis.title.y.left = NULL,
    axis.title.y.right = ggplot2::element_text(angle = -90, margin = ggplot2::margin(l = half_line), vjust = 0),
    axis.text = ggplot2::element_text(size = ggplot2::rel(0.8), colour = bc[3]),
    axis.text.x = ggplot2::element_text(margin = ggplot2::margin(t = 0.8 * half_line / 2), vjust = 1),
    axis.text.x.top = ggplot2::element_text(margin = ggplot2::margin(b = 0.8 * half_line / 2), vjust = 0),
    axis.text.x.bottom = NULL,
    axis.text.y = ggplot2::element_text(margin = ggplot2::margin(r = 0.8 * half_line / 2), hjust = 1),
    axis.text.y.left = NULL,
    axis.text.y.right = ggplot2::element_text(margin = ggplot2::margin(l = 0.8 * half_line / 2), hjust = 0),
    axis.ticks = ggplot2::element_line(colour = bc[3]),
    axis.ticks.x = NULL,
    axis.ticks.x.top = NULL,
    axis.ticks.x.bottom = NULL,
    axis.ticks.y = NULL,
    axis.ticks.y.left = NULL,
    axis.ticks.y.right = NULL,
    axis.ticks.length = ggplot2::unit(half_line / 2, "pt"),
    axis.ticks.length.x = NULL,
    axis.ticks.length.x.top = NULL,
    axis.ticks.length.x.bottom = NULL,
    axis.ticks.length.y = NULL,
    axis.ticks.length.y.left = NULL,
    axis.ticks.length.y.right = NULL,
    axis.line = ggplot2::element_blank(),
    axis.line.x = NULL,
    axis.line.x.top = NULL,
    axis.line.x.bottom = NULL,
    axis.line.y = NULL,
    axis.line.y.left = NULL,
    axis.line.y.right = NULL,

    legend.background = ggplot2::element_rect(fill = bc[1], colour = NA),
    legend.margin = ggplot2::margin(half_line, half_line, half_line, half_line),
    legend.spacing = ggplot2::unit(2 * half_line, "pt"),
    legend.spacing.x = NULL,
    legend.spacing.y = NULL,
    legend.key = ggplot2::element_rect(fill = bc[1], colour = bc[3]),
    legend.key.size = ggplot2::unit(1.2, "lines"),
    legend.key.height = NULL,
    legend.key.width = NULL,
    legend.text = ggplot2::element_text(size = ggplot2::rel(0.8)),
    legend.text.align = NULL,
    legend.title = ggplot2::element_text(hjust = 0),
    legend.title.align = NULL,
    legend.position = "right",
    legend.direction = NULL,
    legend.justification = "center",
    legend.box = NULL,
    legend.box.just = NULL,
    legend.box.margin = ggplot2::margin(0, 0, 0, 0, "cm"),
    legend.box.background = ggplot2::element_blank(),
    legend.box.spacing = ggplot2::unit(2 * half_line, "pt"),

    panel.background = ggplot2::element_rect(fill = bc[1], colour = NA),
    panel.border = ggplot2::element_rect(fill = NA, colour = bc[3], size = 0.5, linetype = "solid"),
    panel.spacing = ggplot2::unit(half_line, "pt"),
    panel.spacing.x = NULL,
    panel.spacing.y = NULL,
    panel.grid = ggplot2::element_line(colour = bc[2]),
    panel.grid.major = ggplot2::element_line(colour = bc[2]),
    panel.grid.minor = ggplot2::element_line(colour = bc[2], size = ggplot2::rel(0.5)),
    panel.grid.major.x = NULL,
    panel.grid.major.y = NULL,
    panel.grid.minor.x = NULL,
    panel.grid.minor.y = NULL,
    panel.ontop = FALSE,

    plot.background = ggplot2::element_rect(colour = bc[1]),
    plot.title = ggplot2::element_text(
      size = ggplot2::rel(1.25),
      face = "bold",
      hjust = 0,
      vjust = 1,
      margin = ggplot2::margin(b = half_line)
    ),
    plot.title.position = "plot",
    plot.subtitle = ggplot2::element_text(
      size = ggplot2::rel(1),
      face = "italic",
      hjust = 0,
      vjust = 1,
      margin = ggplot2::margin(b = half_line)
    ),
    plot.caption = ggplot2::element_text(
      size = ggplot2::rel(0.75),
      face = "italic",
      hjust = 1,
      vjust = 1,
      margin = ggplot2::margin(t = half_line)
    ),
    plot.caption.position = "plot",
    plot.tag = ggplot2::element_text(size = ggplot2::rel(1.25), hjust = 0.5, vjust = 0.5),
    plot.tag.position = "topleft",
    plot.margin = ggplot2::margin(half_line, half_line, half_line, half_line),

    strip.background = ggplot2::element_rect(fill = bc[1], colour = bc[3]),
    strip.background.x = NULL,
    strip.background.y = NULL,
    strip.placement = "inside",
    strip.placement.x = NULL,
    strip.placement.y = NULL,
    strip.text = ggplot2::element_text(
      colour = bc[3],
      size = ggplot2::rel(0.8),
      margin = ggplot2::margin(0.8 * half_line, 0.8 * half_line, 0.8 * half_line, 0.8 * half_line)
    ),
    strip.text.x = NULL,
    strip.text.y = ggplot2::element_text(angle = -90),
    strip.switch.pad.grid = ggplot2::unit(half_line / 2, "pt"),
    strip.switch.pad.wrap = ggplot2::unit(half_line / 2, "pt"),

    complete = TRUE
  )
}
theme_set(theme_black(base_size = 18, base_family = "Alegreya Sans", theme = params[["theme"]]))
theme_update(
  plot.title.position = "plot",
  plot.caption.position = "plot",
  plot.title = element_markdown(),
  plot.subtitle = element_markdown(face = "italic", size = rel(0.80)),
  plot.caption = element_markdown(face = "italic", size = rel(0.65)),
  axis.title.x = element_markdown(),
  axis.text.x = element_markdown(),
  axis.title.y = element_markdown(),
  axis.text.y = element_markdown()
)

options(
  ggplot2.discrete.colour = function(...) scale_colour_viridis_d(..., begin = 0.15, end = 0.85),
  ggplot2.discrete.fill = function(...) scale_fill_viridis_d(..., begin = 0.15, end = 0.85),
  ggplot2.continuous.colour = function(...) scale_colour_viridis_c(..., begin = 0.15, end = 0.85),
  ggplot2.continuous.fill = function(...) scale_fill_viridis_c(..., begin = 0.15, end = 0.85)
)
```

# Introduction

## Subtitle

`some code` and some text

```{r, eval = TRUE, echo = TRUE}
1+1
```

---

# GGPLOT2

```{r}
ggplot(mtcars, aes(wt, mpg)) + geom_point() + labs(title = "GGPLOT2")
```

---
class: inverse, center, middle

# Part 1

---
class: inverse, center, middle

# <img src="https://avatars1.githubusercontent.com/u/8896044?s=460&v=4" height = "150px" id = "picture" />

.pull-left[
<a class="social" href="" target="_blank"><i class="fas fa-phone"></i> +33 (0) 374 00 81 29</a> 
]

.pull-right[
<a class="social" href="mailto:mickael.canouil@cnrs.fr" target="_blank"><i class="fas fa-envelope"></i> mickael.canouil@cnrs.fr</a> 
]

.center[
<a class="social" href="http://m.canouil.fr" target="_blank"><i class="fas fa-home"></i> m.canouil.fr</a> 

<a class="social" href="https://github.com/mcanouil" target="_blank"><i class="fab fa-github"></i> mcanouil</a>
]

.pull-left[
<a class="social" href="https://www.linkedin.com/in/mickael-canouil" target="_blank"><i class="fab fa-linkedin"></i> mickael-canouil</a> 
]

.pull-right[
<a class="social" href="https://twitter.com/mickaelcanouil" target="_blank"><i class="fab fa-twitter"></i> @mickaelcanouil</a>
]
